Efficient and Scalable Bipartite Matching with Fast Beta Linkage (fabl)

### 2021-09-20 methods_paper/fabl-paper.tex
parallel on cluster

@@

@@

>>>>

\hypertarget{accuracy}{%
	\subsection{Accuracy}\label{accuracy}}

@@

\hypertarget{speed}{%
	\subsection{Speed}\label{speed}}

@@

\hypertarget{scale}{%
	\subsection{Scale}\label{scale}}

In one final simulation, we demonstrate how partitioning and hashing the data through \texttt{fabl} greatly expands the scale of the linkage tasks we can solve. Assuming a 16GB personal machine, standard record linkage methods using all-to-all comparisons can only function on tasks where the matrix of comparison vectors $\Gamma$ is less than 8GB. In the context of the above simulation, each comparison vector contains four integers,
